\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{mailto:zara.patel23@gmail.com}{\Large Zara Patel}} & Email : \href{mailto:zara.patel23@gmail.com}{zara.patel23@gmail.com}\\
    Phone : +1 (555) 555-1212 & Age: 27\\
  \end{tabular*}
  
  
  %-----------EDUCATION-----------------
  \section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Name of University}{Location}
        {Degree;  GPA}{Dates Attended}
    \resumeSubHeadingListEnd
  
  
  %-----------EXPERIENCE-----------------
  % re-fill with ONLY working experience, excluding all projects and skills
  \section{Experience}
    \resumeSubHeadingListStart
  
      \resumeSubheading
        {Banana Ink, Silicon Valley}{CTO}{2015-Current}
        \resumeItemListStart
          \resumeItem{Predictive Maintenance}
            {Developed predictive maintenance models using Python and machine learning to predict equipment failures and created a web application to allow technicians to view and schedule maintenance accordingly.}
          \resumeItem{Exploratory Data Analysis}
            {Conducted exploratory data analysis and applied unsupervised learning techniques to segment customers for a retail company using R.}
          \resumeItem{Convolutional Neural Network}
            {Built a convolutional neural network to identify objects in images captured by an autonomous vehicle using Python.}
          \resumeItem{Fraudulent Transactions}
            {Developed a machine learning model to identify fraudulent transactions using Python and incorporated data from multiple sources.}
          \resumeItem{Natural Language Processing}
            {Created a natural language processing system to extract medical concepts from unstructured medical text using Python.}
        \resumeItemListEnd
  
    \resumeSubHeadingListEnd
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Predictive Maintenance Model}
      {Developed predictive maintenance models using Python and machine learning to predict equipment failures and created a web application to allow technicians to view and schedule maintenance accordingly.}
    \resumeSubItem{Exploratory Data Analysis}
     {Conducted exploratory data analysis and applied unsupervised learning techniques to segment customers for a retail company using R.}
    \resumeSubItem{Convolutional Neural Network}
      {Built a convolutional neural network to identify objects in images captured by an autonomous vehicle using Python.}
    \resumeSubItem{Fraudulent Transactions Detection}
      {Developed a machine learning model to identify fraudulent transactions using Python and incorporated data from multiple sources.}
    \resumeSubItem{Natural Language Processing System}
      {Created a natural language processing system to extract medical concepts from unstructured medical text using Python.}
  \resumeSubHeadingListEnd

\section{Programming Skills}
 \resumeSubHeadingListStart
  \resumeSubItem{Languages}
    {Python, R, JavaScript, C++, SQL, Java.}
  \resumeSubItem{Frameworks \& Libraries}
    {scikit-learn, TensorFlow, Keras, NumPy, Pandas, Matplotlib.}
  \resumeSubItem{Technologies}
    {AWS, GCE, React, Kafka.}
 \resumeSubHeadingListEnd

\section{End}
I am an experienced data scientist with strong communication skills and a passion for using data analytics to solve real-world problems. I am eager to bring my enthusiasm and skills to a new role, where I can continue to grow and develop as a professional.

\end{document}

 \end{document}